Is Crime Really On A Rise In Toronto? An Analysis of The Past And Current Crime Rates of Toronto

### 2024-01-19 outputs/paper/paper.qmd
updated readme and paper

---
title: "Is Crime Really On A Rise In Toronto? An Analysis of The Past And Current Crime Rates of Toronto"
author: 
  - Adrian Ly
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "Current mainstream news outlets are pushing a narrative that crime in Toronto is on a rise. "
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-avgcrimerates
#| fig-cap: Average Crime Rates
#| echo: false

@@

```{r}
#| label: fig-percentagecrimerates
#| fig-cap: Average Crime Rates
#| echo: false

@@

# Reading the data
final_percentage_change_table <- read.csv(here::here("outputs/data/percentage_change_table_2014_2023.csv"))
```

@@

percentage_change_table <- read.csv(here::here("outputs/data/percentage_change_table_2022_2023.csv"))
```

@@

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

---
title: "Is Crime Really On A Rise In Toronto? An Analysis of The Past And Current Crime Rates of Toronto"
author: 
  - Adrian Ly
thanks: "Code and data analysis are available at: https://github.com/AdrianUofT/Toronto-Crime-Rates-Investigation.git"
date: today
date-format: long
abstract: "Current mainstream news outlets are pushing a narrative that crime in Toronto is on a rise. Overall crime rates when looking from a macro scale perspective does seem to be increasing on average of about 0.43%, with the micro scale showcasing some crimes such as homicide to have an increase of almost 180%. Using data from OpenDataToronto, this paper serves to present an unbiased review of the current crime rates in Toronto and to reduce any fearmongering that may occur when someone reads a headline. This paper reveals that while crime is technically on a rise, this \"increase\" in crime rate does not necessairly correlate to something worth pointing out."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-avgcrimerates
#| fig-cap: Average Crime Rates
#| echo: false
#| message: false

@@

```{r}
#| label: fig-percentagecrimerates
#| fig-cap: Average Crime Rates
#| echo: false
#| message: false

@@

# Reading the data
final_percentage_change_table <- read.csv(here::here("outputs/data/percentage_change_table_2014_2023.csv"))

final_percentage_change_table |> kable()
```

@@

percentage_change_table <- read.csv(here::here("outputs/data/percentage_change_table_2022_2023.csv"))

percentage_change_table |> kable()
```

@@

 is a trace plot. It shows... This suggests...

 is a Rhat plot. It shows... This suggests...
